Against the Planetary Interpretation of PTFO$\,$8-8695b

### 2020-04-15 paper/ms.tex
update paper. it a photometric binary.
this will need another section!

@@

\begin{abstract}
  PTFO$\,$8-8695b could be the youngest, shortest-period 
  hot Jupiter known.  However it has not been shown to be a planet.
  TESS recently observed PTFO$\,$8-8695 for one month.
  The TESS lightcurve shows that the dominant variability in this
  system is a sinusoidal modulation with a ``long'' period $P_{\rm
  \ell}$
  of 11.96 hours, likely caused by stellar rotation.
  Also present is a complex signal, previously identified as the
  planet candidate, that repeats with a ``short'' period $P_{\rm s}$ of
  10.74 hours.
  The ``long'' and ``short'' signals show the expected beat every 4.48
  days.
  There is a dip in the complex, short-period signal.
  However ground-based photometry from the past decade shows that the
  orbital phase of the dip seems to have instantaneously jumped, at
  least once, and maybe twice.
  The TESS epoch of the dip is consistent with recent observations by
  Tanimoto et al., and differs from the discovery epoch by 5.14 hours.
  Planets do not ``jump'' in orbital phase.
  Given the available evidence,
  PTFO$\,$8-8695 seems consistent with the
  ``transient dipping'' phenomenology observed in many young M dwarfs.
  It seems rather unlikely to be a planet.
\end{abstract}

@@

\section{Introduction}
If PTFO$\,$8-8695b were a planet, it would be exceptional.
A transiting hot Jupiter, orbiting a $\approx$3$\,$Myr old M dwarf
in ORION would make it the youngest hot Jupiter known.
Its orbital period of only 12 HOURS would also make it the shortest
period hot Jupiter known.

@@

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf TESS lightcurve of PTFO 8-8695 (Sector 6, Orbit 19).}
		{\it Top}: ``Raw'' \texttt{PDCSAP} mean-subtracted relative flux
		versus time. The beat period of 4.48 days is visible by eye.  The
		model plotted underneath the data includes 2 harmonics at the long
		period $P_{\rm \ell}$, plus 2 harmonics and a transit at the short
		period $P_{\rm s}$.
		{\it Upper middle}: Long-period signal, equal to the raw signal
		minus the short-period signal.
		{\it Lower middle}: Short-period signal, equal to the raw signal
		minus the long-period signal.
		{\it Bottom}: residual.  The data are binned from 2 to 10 minute
		cadence as a convenience for plotting and fitting.
		\label{fig:splitsignal}
	}
\end{figure*}

%\newpage
\begin{figure*}[hbtp]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf TESS lightcurve of PTFO 8-8695 (Sector 6, Orbit 20).}
		Panels are as in Figure~\ref{fig:splitsignal}.
		\label{fig:splitsignalii}
	}
\end{figure*}
%\newpage

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene used for blend analysis.}
		{\it Top:} Mean TESS image of PTFO 8-8695 over Sector~6, with a
		log-stretch.  The position of PTFO 8-8695 is shown with a yellow
		star.  Neighbors with $T<17$ are shown with orange crosses.  The
		apertures used to measure the background and target star flux are
		shown with \texttt{X} and \texttt{/} hatches, respectively.
		{\it Bottom:} Digitized Sky Survey $R$-band image of the same
		field, with a linear stretch. The circles show apertures of radii
		1, 1.5, and 2.25 pixels used in part of our blend analysis.  The
		pixel level TESS data show that ``Star A''  does not contribute
		variability at either of the two observed periods (see
		Section~\ref{subsec:blend}).
		\label{fig:scene}
	}
\end{figure}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Timing residuals for PTFO 8-8695b from a decade of monitoring.}
		Black points are times of ``dips'', minus the indicated linear
		ephemeris.  The $y$-axis is given in units of phase for the
		short-period signal.  The star shows the binned TESS ephemeris.
		``Dips'' have been observed by \citet{van_eyken_ptf_2012},
		\citet{ciardi_follow-up_2015}, \citet{yu_tests_2015},
		\citet{raetz_yeti_2016}, \citet{onitsuka_multi-color_2017}, and
		\citet{tanimoto_evidence_2020}.  Certain dips ({\it e.g.}, the one
		at phase 0 in mid-2019) are consistent with noise, and were likely
		reported because something was {\it expected}, rather than
		convincingly {\it observed}.  Horizontal dashed lines are drawn at
		$\pm (P_{\rm \ell} - P_{\rm s})/P_{\rm s}$, highlighting what
		could be either a numerical coincidence or an observational bias.
		The orbital phase observed by TESS is consistent with that of
		\citet{tanimoto_evidence_2020}, and quite different from the
		original phase.
		\label{fig:o_minus_c}
	}
\end{figure*}

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f6_comp.png}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf foo.}
		bar
		\label{fig:corner}
	}
\end{figure*}

\subsection{Observations}

PTFO 8-8695 was observed by TESS with Camera 1, CCD 1, from December
15, 2018 to January 6, 2019, during the sixth sector of science
operations.  The star was designated TIC 264461976 in the TESS Input
Catalog \citep{stassun_TIC_2018,stassun_TIC8_2019}.  The pixel data
for an $11\times11$ array surrounding PTFO 8-8695 were averaged into
2-minute stacks by the onboard computer.  Each 2048$\times$2048 image
from the CCD was also averaged into 30-minute stacks, and saved as a
``full frame image'' (FFI).

The 2-minute stacks for PTFO 8-8695 were then reduced to lightcurves
by the Science Processing Operations Center (SPOC) at NASA
Ames~\citep{jenkins_tess_2016}.  Our main analysis used the resulting
Presearch Data Conditioning (PDC) lightcurve.  The PDC lightcurve
aperture used pixels chosen to maximize the SNR of the total flux of
the target \citep{smith_kepler_apertures_2017}.  Non-astrophysical
variability was removed through the methods discussed by
\citet{smith_kepler_PDC_2017}.

As an independent check on the shorter cadence SPOC light-curve, we
separately processed the 30-minute image stacks as part of the Cluster
Difference Imaging Photometric Survey (CDIPS;
\citep{bouma_cluster_2019}).  The CDIPS lightcurve used a circular
aperture with radius 1 pixel.

@@

\subsection{Visual Inspection}

@@

\section{The Model}
\label{sec:analysis}

\subsection{Model Description}

@@

We implemented and fitted the models using \texttt{PyMC3}, which is
built on \texttt{theano}
\citep{salvatier_2016_PyMC3,exoplanet:theano}.  For the Fourier terms,
we used the default math operators.  For the exoplanet transit, we
used the model and derivatives implemented in \texttt{exoplanet}
\citep{exoplanet:exoplanet}.  Our priors are listed in
Table~\ref{tab:posterior}.  To speed up the fitting, we binned the
cleaned 2 minute lightcurves to 10 minute bins.  We correspondingly
scaled the uncertainties in the flux measurements by a factor of
$\sqrt{5}$.  Before sampling, we initialized each model to the maximum
a posteriori (MAP) solution.  We then sampled using \texttt{PyMC3}'s
gradient-based No-U-Turn Sampler \citep{hoffman_no-u-turn_2014}, and
used $\hat{R}$ as our convergence diagnostic
\citep{gelman_inference_1992}.
We tested our ability to successfully recover injected parameters
using synthetic data, before switching to the actual PTFO 8-8695
lightcurves.

\subsection{Fitting Results}

@@

The target star, PTFO 8-8605 (TIC 264461976), has a $T$-band magnitude
of 14.0, and its position is shown with a star.  The other (unlabeled)
star inside the target aperture, TIC 264461979, has $T=16.8$ and so
cannot contribute a signal with relative amplitude 10\%.  The only
neighbor that is sufficiently close and bright that its light might
contaminate the target star is TIC 264461980, with $T=14.8$, which we
denote ``Star A''.  Star A is 23.6'' NW of our target, and based on
the magnitude difference could contribute up to 48\% the flux of our
target star, PTFO 8-8695.

Because PTFO 8-8695 has previously been identified to have periodicity
consistent with our measurement of $P_{\rm s}$, our main concern
regarding blending is the degree to which we can be certain that the
long-period signal at $P_{\rm \ell}$ also originates from PTFO 8-8695.
We took two approaches towards determining the source of the
long-period signal.

@@

Second, we examined the lightcurve of each pixel in the scene
individually.  We opted to use the interactive tools implemented in
\texttt{lightkurve} \citep{lightkurve_2018}.  If Star A were the
source of the long-period variability, we would expect the pixels
nearest to Star A to show a sinusoidal signal with amplitude exceeding
$10\%$.  We find no evidence for this being the case.  The pixel
directly below Star A does not clearly show the sinusoidal
variability, and the peak-to-peak variability in that pixel is
$\lesssim 8\%$.  In contrast, the south-easternmost pixel within PTFO
8-8695's aperture (the pixel furthest from Star A that was used in the
optimal aperture) shows the $P_{\rm \ell}$ sinusoidal variability
signal at $\approx 10\%$ amplitude.

As there is no evidence in favor of a blend scenario, we conclude that
both the $P_{\rm s}$ and $P_{\rm \ell}$ signals originate from PTFO
8-8695.

@@

\subsection{Short period out-of-dip modulation}
If there were a giant planet transiting PTFO 8-8695, it would tidally
distort the host star, and cause ellipsoidal photometric modulations.
The amplitude of the ellipsoidal distortion for a $1\,M_{\rm Jup}$
companion would be about 1400$\,$ppm
\citep{shporer_astrophysics_2017}.  This is significantly larger than
the typical ellipsopidal modulation induced by close-in giant planets
because the host star is puffy, and still on the pre-main-sequence.
For our estimate, we assumed $R_\star = 1.39 R_\odot$, and $M_\star =
0.39 M_\odot$ \citep{van_eyken_ptf_2012}.

@@

PTFO 8-8695 was previously thought to potentially host a hot Jupiter.
The TESS lightcurve of PTFO 8-8695 showed a number of new features,
many of which seem to disfavor the hot Jupiter interpretatation.
The TESS data showed two key pieces of evidence.
\begin{enumerate}
  \item {\it Two periodic signals.} The ``long'' signal is a 10\%
      peak-to-peak sinusoidal modulation repeating every 11.96 hours.
      The ``short'' signal is a 4\% peak-to-peak complex modulation
      repeating every 10.74 hours. It is composed of a dip, plus at
      least two harmonics. The signals beat, and therefore cannot be
      an artifact linked to data processing.
  \item {\it A dip at the wrong orbital phase.} The clearest dip in
    the ``short'' signal was consistent with recent observations by
    \citet{tanimoto_evidence_2020}, and differed from the discovery
    epoch by 5.14 hours.
\end{enumerate}

The physical mechanism responsible for all these features remains a
matter of speculation.
With that said, the TESS data support new arguments against the planetary
interpretation of PTFO 8-8695.
First, if the long signal is caused by starspot modulation, and the
short signal by a transiting planet, what causes the additional
complex modulations seen at the short, ``orbital'', period?

>>>>

\newcommand{\ptfo}{PTFO$\,$8-8695}
\newcommand{\ptfob}{PTFO$\,$8-8695b}

@@

\begin{abstract}
  PTFO$\,$8-8695b, a candidate hot Jupiter in the 7--10$,$Myr old
  Orion-OB1a cluster, might be the youngest hot Jupiter known.
  We inspected data from TESS and Gaia to clarify whether it is
  actually a planet.
  The TESS lightcurve shows that the dominant variability in this
  system is a sinusoidal modulation with a ``long'' period $P_{\rm
  \ell}=11.96\,$hr, likely caused by stellar rotation.  Also present
  is a complex signal, previously identified as the planet candidate,
  that repeats with a ``short'' period $P_{\rm s}= 10.74\,$hr.
  The ``long'' and ``short'' signals beat every 4.48 days.
  Although there is a dip in the short-period signal, ground-based
  photometry from the past decade shows that the orbital phase of the
  dip seems to have instantaneously jumped, at least once, and perhaps
  twice.
  Planets do not ``jump'' in orbital phase.
  Furthermore, the Gaia data show that PTFO$\,$8-8695 is probably
  a photometric binary (the comparison is made relative to the
  kinematic subgroup of 25-Ori for which PTFO$\,$8-8695 is a member).
  Given the available evidence, we believe that PTFO$\,$8-8695 is a
  binary M dwarf system in which one star is showing the ``long''
  rotation signal, and the other star is showing ``transient dipping''
  that has been observed in many young M dwarfs.
  The planetary interpretation seems highly unlikely.
\end{abstract}

@@

\section{Introduction}
If \ptfob\ were a planet, it would be exceptional.
A transiting hot Jupiter, orbiting a $\approx$3$\,$Myr old M dwarf
in ORION would make it the youngest hot Jupiter known.
Its orbital period of only 12 HOURS would also make it the shortest
period hot Jupiter known.

@@

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf TESS lightcurve of \ptfo\ (Sector 6, Orbit 19).}
		{\it Top}: ``Raw'' \texttt{PDCSAP} mean-subtracted relative flux
		versus time. The beat period of 4.48 days is visible by eye.  The
		model plotted underneath the data includes 2 harmonics at the long
		period $P_{\rm \ell}$, plus 2 harmonics and a transit at the short
		period $P_{\rm s}$.
		{\it Upper middle}: Long-period signal, equal to the raw signal
		minus the short-period signal.
		{\it Lower middle}: Short-period signal, equal to the raw signal
		minus the long-period signal.
		{\it Bottom}: residual.  The data are binned from 2 to 10 minute
		cadence as a convenience for plotting and fitting.
		\label{fig:splitsignal}
	}
\end{figure*}

\begin{figure*}[hbtp]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf TESS lightcurve of \ptfo\ (Sector 6, Orbit 20).}
		Panels are as in Figure~\ref{fig:splitsignal}.
		\label{fig:splitsignalii}
	}
\end{figure*}

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene used for blend analysis.}
		{\it Top:} Mean TESS image of \ptfo\ over Sector~6, with a
		log-stretch.  The position of \ptfo\ is shown with a yellow
		star.  Neighbors with $T<17$ are shown with orange crosses.  The
		apertures used to measure the background and target star flux are
		shown with \texttt{X} and \texttt{/} hatches, respectively.
		{\it Bottom:} Digitized Sky Survey $R$-band image of the same
		field, with a linear stretch. The circles show apertures of radii
		1, 1.5, and 2.25 pixels used in part of our blend analysis.  The
		pixel level TESS data show that ``Star A''  does not contribute
		variability at either of the two observed periods (see
		Section~\ref{subsec:blend}).
		\label{fig:scene}
	}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.5\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Timing residuals for \ptfob\ from a decade of monitoring.}
		Black points are times of ``dips'', minus the indicated linear
		ephemeris.  The $y$-axis is given in units of phase for the
		short-period signal.  The star shows the binned TESS ephemeris.
		``Dips'' have been observed by \citet{van_eyken_ptf_2012},
		\citet{ciardi_follow-up_2015}, \citet{yu_tests_2015},
		\citet{raetz_yeti_2016}, \citet{onitsuka_multi-color_2017}, and
		\citet{tanimoto_evidence_2020}.  Certain dips ({\it e.g.}, the one
		at phase 0 in mid-2019) are consistent with noise, and were likely
		reported because something was {\it expected}, rather than
		convincingly {\it observed}.  Horizontal dashed lines are drawn at
		$\pm (P_{\rm \ell} - P_{\rm s})/P_{\rm s}$, highlighting what
		could be either a numerical coincidence or an observational bias.
		The orbital phase observed by TESS is consistent with that of
		\citet{tanimoto_evidence_2020}, and quite different from the
		original phase.
		\label{fig:o_minus_c}
	}
\end{figure}

%\begin{figure*}[t!]
%	\begin{center}
%		\leavevmode
%		\includegraphics[width=0.9\textwidth]{f6_comp.png}
%	\end{center}
%	\vspace{-0.7cm}
%	\caption{ {\bf foo.}
%	bar
%		\label{fig:corner}
%	}
%\end{figure*}

\subsection{TESS Observations}

\ptfo\ was observed by TESS with Camera 1, CCD 1, from December
15, 2018 to January 6, 2019, during the sixth sector of science
operations \citep{ricker_transiting_2015}.  The star was designated
TIC 264461976 in the TESS Input Catalog
\citep{stassun_TIC_2018,stassun_TIC8_2019}.  The pixel data for an
$11\times11$ array surrounding \ptfo\ were averaged into 2-minute
stacks by the onboard computer.  Each 2048$\times$2048 image from the
CCD was also averaged into 30-minute stacks, and saved as a ``full
frame image'' (FFI).

The 2-minute stacks for \ptfo\ were then reduced to lightcurves
by the Science Processing Operations Center (SPOC) at NASA
Ames~\citep{jenkins_tess_2016}.  Our main analysis used the resulting
Presearch Data Conditioning (PDC) lightcurve.  The PDC lightcurve
aperture used pixels chosen to maximize the SNR of the total flux of
the target \citep{smith_kepler_apertures_2017}.  Non-astrophysical
variability was removed through the methods discussed by
\citet{smith_kepler_PDC_2017}.

As an independent check on the shorter cadence SPOC light-curve, we
separately processed the 30-minute image stacks as part of the Cluster
Difference Imaging Photometric Survey (CDIPS;
\citealt{bouma_cluster_2019}).  The CDIPS lightcurve used a circular
aperture with radius 1 pixel.

@@

\subsection{Gaia Observations}

Between July 25, 2014 and May 23, 2016, Gaia acquired 121 ``good''
observations of \ptfo, {\it i.e.}, observations that were not strongly
downweighted in the astrometric solution of the source (CITE).
%TODO: give an original explanation of how Gaia works
The Gaia data processing team at XXXINSTITUTION combined the XXX and
YYY into a global astrometric solution, from which the parallax of 
\ptfo\ was derived (CITE).
The star was assigned a Gaia DR2 identifier of 3222255959210123904
(CITE).
In addition, measurements of the stellar proper motion between
observation epochs were made.

One point of note:
Gaia DR2 measured a significant ``astrometric excess'', at a level of
10.3$\sigma$.
This astrometric excess indicates the degree
to which a single-source model fails to explain the observed astrometric
measurements (CITE).

\subsection{Cluster Membership}
The Orion molecular cloud complex has numerous subgroups, with ages
spanning 1 to 15$\,$Myr (CITE).
\ptfo\ has been known to be a member of the Orion OB1a association
since at least CITE (Briceno 2005).
Its relation to the broader Orion complex has been further explored by
CITEX, CITEY, and CITEZ (Briceno 05, 08, 18, whomever Van Eyken cites,
and Kounkel 18).

In describing the cluster membership of \ptfo, we
follow the notation and results of \citet{kounkel_apogee2_2018}.
\citet{kounkel_apogee2_2018} combined astrometric data from Gaia DR2
with spectroscopic data from APOGEE-2 (CITE).
They then performed a hierarchical clustering on the six dimensional
position and velocity information to identify subgroups within the
Orion complex.
From smallest to largest groups, \ptfo\ was identified as being a
member of the following subgroups:
\begin{equation}
  {\rm PTFO\,8\text{-}8695}
  \in {\rm 25\,Ori\text{-}1}
  \subset {\rm 25\,Ori}
  \subset {\rm Orion\ OB1a}
  \subset {\rm Orion\ D},
\end{equation}
where from set-notation, `$\subset$' denotes ``is a proper subset of''.

While all members of the Orion complex are young relative to the field, the internal
age dispersion between different subgroups is measurable.
The Orion Nebula Cluster (M42) is a site of ongoing star-formation, and its
stars are 1-3$\,$Myr old (CITE).
25$\,$Ori\-1, by contrast, is XX-XX$\,$Myr old (CITE).
These details are essential when assessing any evidence for photometric binarity
in \ptfo, because there is a degeneracy between stellar luminosity
and age for stars on the pre-main-sequence.
Having a clean sample of tightly spatially and kinematically associated stars
is essential to minimize contamination not just from the field, but from older and younger
members of the Orion complex itself.

\section{TESS Analysis}
\label{sec:analysis}

\subsection{Inspection}

@@

\subsection{ Model}

@@

We implemented and fitted the models using \texttt{PyMC3}, which is
built on \texttt{theano}
\citep{salvatier_2016_PyMC3,exoplanet:theano}.  For the Fourier terms,
we used the default math operators.  For the exoplanet transit, we
used the model and derivatives implemented in \texttt{exoplanet}
\citep{exoplanet:exoplanet}.  Our priors are listed in
Table~\ref{tab:posterior}.  To speed up the fitting, we binned the
cleaned 2 minute lightcurves to 10 minute bins.  We correspondingly
scaled the uncertainties in the flux measurements by a factor of
$\sqrt{5}$.  Before sampling, we initialized each model to the maximum
a posteriori (MAP) solution.  We then sampled using \texttt{PyMC3}'s
gradient-based No-U-Turn Sampler \citep{hoffman_no-u-turn_2014}, and
used $\hat{R}$ as our convergence diagnostic
\citep{gelman_inference_1992}.
We tested our ability to successfully recover injected parameters
using synthetic data, before switching to the actual \ptfo\
lightcurves.

\subsection{ Fitting Results}

@@

The target star, \ptfo\ (TIC 264461976), has a $T$-band magnitude
of 14.0, and its position is shown with a star.  The other (unlabeled)
star inside the target aperture, TIC 264461979, has $T=16.8$ and so
cannot contribute a signal with relative amplitude 10\%.  The only
neighbor that is sufficiently close and bright that its light might
contaminate the target star is TIC 264461980, with $T=14.8$, which we
denote ``Star A''.  Star A is 23.6'' NW of our target, and based on
the magnitude difference could contribute up to 48\% the flux of our
target star, \ptfo.

Because \ptfo\ has previously been identified to have periodicity
consistent with our measurement of $P_{\rm s}$, our main concern
regarding blending is the degree to which we can be certain that the
long-period signal at $P_{\rm \ell}$ also originates from \ptfo.
We took two approaches towards determining the source of the
long-period signal.

@@

Second, we examined the lightcurve of each pixel in the scene
individually.  We opted to use the interactive tools implemented in
\texttt{lightkurve} \citep{lightkurve_2018}.  If Star A were the
source of the long-period variability, we would expect the pixels
nearest to Star A to show a sinusoidal signal with amplitude exceeding
$10\%$.  We find no evidence for this being the case.  The pixel
directly below Star A does not clearly show the sinusoidal
variability, and the peak-to-peak variability in that pixel is
$\lesssim 8\%$.  In contrast, the south-easternmost pixel within \ptfo's aperture (the pixel furthest from Star A that was used in the
optimal aperture) shows the $P_{\rm \ell}$ sinusoidal variability
signal at $\approx 10\%$ amplitude.

As there is no evidence in favor of a blend scenario, we conclude that
both the $P_{\rm s}$ and $P_{\rm \ell}$ signals originate from \ptfo.

\section{Gaia Analysis}
\label{sec:gaia}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f6.png}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Positions, kinematics, and HR diagram of \ptfo.}
	Members of the 25$\,$Ori-1 subgroup are shown with black circles, and were identified by \citet{kounkel_apogee2_2018} through clustering on Gaia-DR2 and APOGEE data.
	The ``neighborhood'' (gray circles) is defined as the group of at most $10^4$ randomly selected non-member stars within 5 standard deviations of the mean right ascension, declination, and parallax.
	\label{fig:gaia}
	}
\end{figure*}

We did an analysis.
The result was
Figure~\ref{fig:gaia}.

@@

\subsection{Short period out-of-dip modulation}
If there were a giant planet transiting \ptfo, it would tidally
distort the host star, and cause ellipsoidal photometric modulations.
The amplitude of the ellipsoidal distortion for a $1\,M_{\rm Jup}$
companion would be about 1400$\,$ppm
\citep{shporer_astrophysics_2017}.  This is significantly larger than
the typical ellipsopidal modulation induced by close-in giant planets
because the host star is puffy, and still on the pre-main-sequence.
For our estimate, we assumed $R_\star = 1.39 R_\odot$, and $M_\star =
0.39 M_\odot$ \citep{van_eyken_ptf_2012}.

@@

\ptfo\ was previously thought to potentially host a hot Jupiter.
The TESS lightcurve of \ptfo\ showed a number of new features,
many of which seem to disfavor the hot Jupiter interpretatation.
The TESS data showed two key pieces of evidence.
\begin{enumerate}
  \item {\it Two periodic signals.} The ``long'' signal is a 10\%
      peak-to-peak sinusoidal modulation repeating every 11.96 hours.
      The ``short'' signal is a 4\% peak-to-peak complex modulation
      repeating every 10.74 hours. It is composed of a dip, plus at
      least two harmonics. The signals beat, and therefore cannot be
      an artifact linked to data processing.
  \item {\it A dip at the wrong orbital phase.} The clearest dip in
    the ``short'' signal was consistent with recent observations by
    \citet{tanimoto_evidence_2020}, and differed from the discovery
    epoch by 5.14 hours.
\end{enumerate}

The physical mechanism responsible for all these features remains a
matter of speculation.
With that said, the TESS data support new arguments against the planetary
interpretation of \ptfo.
First, if the long signal is caused by starspot modulation, and the
short signal by a transiting planet, what causes the additional
complex modulations seen at the short, ``orbital'', period?
